---
title: "Prices of Furniture and Tables at IKEA"
subtitle: "A Tidytuesday project"
author: "S.Soundarya"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
```

# TidyTuesday Week 45 IKEA Furniture

## Read data



```{r,warning=FALSE,message=FALSE}
ikea <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-03/ikea.csv')
```

## Check data

```{r}
dim(ikea)
names(ikea)
str(ikea)
```

## Categories of furniture
```{r}
table(ikea$category)
```
^[Looks like Tables & desks category has the highest number, let me pick this for building regression models]

# Load libraries
```{r,message=FALSE,warning=FALSE}
library(tidyverse)
```


# Making subset of the data

```{r}
ikea_tabdesk<- ikea %>%
  filter(category=="Tables & desks")
dim(ikea_tabdesk)
head(ikea_tabdesk)
```


# Building regression models  

## Does online availability determine the price of the item?
```{r}
model1<- lm(price~sellable_online,data = ikea_tabdesk)
summary(model1)
```

^[No, having an online presence doesnt influence the price]  

## Does availbility of color choices determine the price of the item?

```{r colorchoices fig-margin, fig.margin = TRUE, fig.cap = "Price of the product based on color availability.", fig.width=3.5, fig.height=3.5, cache=TRUE, message=FALSE,warning=FALSE}
library(ggpubr)
library(ggthemes)
ggplot(ikea_tabdesk, aes(other_colors,price)) +
  geom_boxplot()+
  stat_compare_means()+
  theme_tufte()
model2<- lm(price~other_colors,data = ikea_tabdesk)
summary(model2)
```


^[wow, yes, looks like color choices are related to price,i.e. if colors are available, the product is priced lower]  

## What about height, width and depth of the item  

### Height of the item and its price

```{r height fig-margin, fig.margin = TRUE, fig.cap = "Taller items are priced more (marginal significance) ", fig.width=3.5, fig.height=3.5, cache=TRUE, message=FALSE,warning=FALSE}
ggplot(ikea_tabdesk, aes(height,price)) +
  geom_point()+
  geom_smooth(method = "lm",se=FALSE)+
  stat_cor()+
  theme_tufte()
model3<- lm(price~height, data = ikea_tabdesk)
summary(model3)
```
### Width of the item and its price


```{r width fig-margin, fig.margin = TRUE, fig.cap = "Wider items are more priced!", fig.width=3.5, fig.height=3.5, cache=TRUE, message=FALSE,warning=FALSE}
ggplot(ikea_tabdesk, aes(width,price)) +
  geom_point()+
  geom_smooth(method = "lm",se=FALSE)+
  stat_cor()+
  theme_tufte()
model4<- lm(price~width, data = ikea_tabdesk)
summary(model4)
```

### Depth of the item and its price


```{r depth fig-margin, fig.margin = TRUE, fig.cap = "Deeper items are more priced!", fig.width=3.5, fig.height=3.5, cache=TRUE, message=FALSE,warning=FALSE}
ggplot(ikea_tabdesk, aes(depth,price)) +
  geom_point()+
  geom_smooth(method = "lm",se=FALSE)+
  stat_cor()+
  theme_tufte()
model5<- lm(price~depth, data = ikea_tabdesk)
summary(model5)
```


```{r}
library(stargazer)
fullmodel<- lm(price~other_colors+height+depth+width,data=ikea_tabdesk)
summary(fullmodel)
confint(fullmodel)
```

```{r}
stargazer(model2,model3,model4,model5,fullmodel,
          type = "text",
          column.labels = c("Colors Available", "height","width","depth", "Additive Model"),
          ci = TRUE,model.numbers = FALSE,
          intercept.bottom = FALSE,
          out = "newreg_td.txt",title = "What determines the price of tables&desks at IKEA?")

```

## Visualizing coefficients

```{r,warning=FALSE,message=FALSE,fig.width=10, fig.height=3, fig.fullwidth=TRUE}
library(jtools)
plot_summs(model2,model3,model4,model5,fullmodel,inner_ci_level = 0.9,scale=TRUE,
           model.names = c("colors", "height", "width", "depth", "Additive model"),
           legend.title = "What determines the Price of Tables & Desks at IKEA?")
```

^[I excluded online availability from the model, but included height since it was marginally significant.]  

`r newthought('In the additive model')`^[Note depth loses significance in the additive model], the item is priced higher  

  -- if there is availability of colors,   
  -- if it is a taller item &  
  -- if it is a wider item  


